Viscous Transport in Eroding Porous Media

### 2019-05-06 docs/transport/erosion_transport.tex
doing in tranposrt paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation Methods}
\label{sec:fmm}
{\color{red}
To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

@@

{\color{red}
 Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
where $\alpha_2$ is a constant.

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}
{\color{red} Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation Methods}
\label{sec:fmm}

{\color{red}
To numerically approach the nearly singular integraton by using Barycentric quadrature rule,

To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

@@

{\color{red}
 Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
\begin{equation}\label{eqn:Cw2b}
d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}
\end{equation}
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
\begin{equation}\label{eqn:Cb2b}
d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)
\end{equation}
where $\alpha_2$ is a constant.

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly

{\color{red} \item Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency

To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$. To check the accuracy of the simulations, we use (?)
To see how efficient our code is, we record the cpu time for each step.

}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
{\color{red} We first consider a circular body in a shear flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow form the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the initial minimum distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
{\color{red} To 
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
